Effects of the body force on the evacuation dynamics

### 2019-12-18 paper.tex
escribi texto que explica el primer grafico

>>>>

In this section, we present the results corresponding to the bottleneck geometry. We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\

Fig. \ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity. The evacuation time was defined as the time until 70\% of the pedestrians left the room. The different markers correspond to different $k$ values ($i.e$ different body force stiffness). The crosses correspond to the Helbing original SFM parameter, the up triangles correspond to the value measured in Ref .. and Increasing the $k$ reduced the evacuation time, squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM). The down triangles correspond to an intermediate value between the empirical value presented in Ref... and the chosen by Helbing in Ref...\\

There is a noticeable difference in the evacuation time depending on the $k$ value of the body force. The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer the overall speed increases (hence the evacuation time).\\

Notice that the faster-is-slower (FIS) effect and the faster-is-faster (FIF) effect are both dependent on the value of $k$. If $k$ is high enough, the FIF effect does not show for the explored desired velocity values ($v_d \leq 10$~m/s).\\
